Spatial Analysis

### 2021-08-09 Scripts/spatial_analisis.Rmd
updated website for presentation

---
title: "Spatial Analysis"
author: "Juliano Palacios Abrantes"
output:
  html_document:
  # html_notebook:
    fig_width: 6
    fig_height: 4
    code_folding: hide
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
    theme: darkly
---

@@

# Load grid df
grid_eez_df <- my_path("D","Spatial","grid_eez_df.csv", read = T)

@@

spp_runs <- tibble(taxa = (list.files(my_path("R","Partial/Interpolation")))) %>%
  mutate(
    taxa = str_remove(taxa, "tif_"),
    taxa = str_remove(taxa, ".csv"),
    taxa = str_replace(taxa, "_", " ")
  )

@@

# single species run
# run_tis(input_data = ocean_data,
#         grid = grid_eez_df,
#         years = years,
#         reg = regions,
#         taxa = "Illex illecebrosus"
# )

# Run them all in parallel
lapply(spp,
                   run_tis, 
                   input_data = ocean_data,
                   grid = grid_eez_df,
                   years = years,
                   reg = regions
)

>>>>

---
title: "Spatial Analysis"
author: "Juliano Palacios Abrantes"
output:
  # html_document:
  html_notebook:
    fig_width: 6
    fig_height: 4
    code_folding: hide
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
    theme: darkly
---

@@

# Load grid df
# For fishing ports
grid_eez_fp_df <- my_path("D","Spatial/grid_eez_fp_sf","grid_eez_fp_df.csv", read = T)

# For state waters
# grid_eez_sw_df <- my_path("D","Spatial/grid_eez_fp_sf","grid_eez_fp_df.csv", read = T)

@@

spp_runs <- tibble(taxa = (list.files(my_path("R","Partial/Interpolation/fp")))) %>%
  mutate(
    taxa = str_remove(taxa, "tif_"),
    taxa = str_remove(taxa, ".csv"),
    taxa = str_replace(taxa, "_", " ")
  )

@@

# # single species run
# run_tis(input_data = ocean_data,
#         grid = grid_eez_fp_df,
#         years = years,
#         reg = regions,
#         taxa = "Illex illecebrosus",
#         method = "fp"
# )

# Run them all in parallel
lapply(spp,
       run_tis, 
       input_data = ocean_data,
       grid = grid_eez_fp_df,
       years = years,
       reg = regions,
       method = "fp"
)
